---
title: "Group_01_Project2_demo"
author: "Group_01"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: no
    keep_tex: true
  html_document:
    df_print: paged
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

```{r libraries}
library(tidyverse)
library(moderndive)
library(skimr)
library(kableExtra)
library(gridExtra)
library(broom)
library(plotly)
library(GGally)
library(sjPlot)
library(janitor)
library(leaps)
library(jtools)
library(ggstance)
```

```{r data, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
data <- read.csv("dataset1.csv")
data<-data[,-2] #remove region column as all entries the same
data$Total.Household.Income<-data$Total.Household.Income/(1e4)
data$Total.Food.Expenditure<-data$Total.Food.Expenditure/(1e4) 
#scaling the income and expenditure variables to be measured in 10000 Phillipine Pesos to make scales on later plot axes easier to read
```

# Introduction {#sec:Intro}

Data come from the FIES (Family Income and Expenditure Survey) recorded in the Philippines. The survey, which is undertaken every three years, is aimed at providing data on family income and expenditure. The data obtained from this survey are from different regions across the Philippines. This report will focus on one individual area, the Cordillera Administrative Region and so region has been removed from the dataset as it will not be informative as an explanatory variable.

The report will investigate which household related variables influence the number of people living in a household. The data used consists of 1725 observations of ten variables, two of which are categorical and the remaining are numerical. 

# Exploratory Data Analysis {#sec:EDA}

Figure 1 shows the distribution of the response variable: Number of members in a household (variable name "Total.number.of.family.members"). The modal response is 4 members and the distribution is right-skewed,

```{r distribution of response variable, eval = TRUE, fig.align='center', out.width='80%', fig.pos = "H", fig.cap="Distribution of Response Variable"}
barplot1<- ggplot(data, aes(x=Total.Number.of.Family.members))+ 
  geom_bar(color = "white", fill="royalblue1") +
  theme(legend.position="none", plot.title=element_text(hjust=0.5))+
      labs(x ="Number of Members in a Household", title = "Distribution of Number of Members of Households in the CAR Region");barplot1
```

The summary below shows the count data for each level of the response variable and the percentage of total households in the region in each group.

```{r data.score}
data.score <- data %>%
  dplyr::select(Total.Number.of.Family.members,Total.Household.Income,
                Total.Food.Expenditure, Household.Head.Age, House.Floor.Area, House.Age,
                Number.of.bedrooms, Electricity)
```

Table 1 shows summary data for all the numerical variables.There is no missing data within these variables and so no values will need to be imputed for the analysis in the report.
The response variable, total number of family members in a household, ranges from 1 to 15, with the middle 50% of number of family members falling between 3 and 6 also an average number of family members of 4.67. 
There appear to be possible outliers at the maximum values of Total Household Income and House Floor Area. The total household income is range from 11988 to 6042860 Philippine Peso. The middle 50% of total household income is between 118565 and 328335, with an income of 269540.48 peso on average. 
The third variable is total food expenditure, in Phillipine peso, which is the range of 6781 to 327724, with the middle 50% lies between 51922 and 98493. Then, the household head's age is range from 17 to 99 years, with the middle 50% falling between 41 and 63 years of age. Next, the house floor area is range from 5 to 900 square metres. The central 50% of the variable house floor area is between 32 and 102 with an average area of 90.92. The sixth explanatory variable is the house (building) age and it ranges in value from 0 to 100, with the middle 50% falling between 12 and 31. The number of bedrooms in the house ranges from 0 to 9 with a mean average number of bedrooms of 2.26 per household. Finally, we may look at the binary variable electricity, which denotes whether the property has electricity access or not, the average score of electricity is 0.93, which means 93% household have electricity.

```{r numerical summaries}
my_skim <- skim_with(numeric = sfl(hist = NULL))
my_skim(data.score)  %>%
  dplyr::select(-skim_type) %>%
  as_tibble() %>%
  kable(col.names = c("Variable", "Missing", "Complete", "Mean", "SD", "Min.", "1st Q.",
                      "Median", "3rd Q.", "Max."),
        caption = "Summary statistics of numerical variables",
        booktabs = TRUE,  digits = 2) %>%
  kable_styling(font_size = 10, latex_options = "scale_down") 
#create a summarized statistics table for all variables
```

The correlation coefficient between all numerical variables are shown in Table 2. There is a moderate positive correlation (0.611) between the total household income and the household food expenditure. Additionally there is a slight positive correlation between the total household income and the number of bedrooms in the household (0.441) and the number of family members and total food expenditure (0.469). The other variables are all weakly correlated.The correlation coefficient between household Head's age, house floor area, house age and total number of family members are negative, which shows the rise of those three variables will lead to a reduction in the expected number of family members in a household.

```{r correlation}
data.score %>%
  cor() %>%
  kable(caption = 'Correlation of all variables.',booktabs = TRUE, digits = 3) %>%
  kable_styling(font_size = 10, latex_options = "scale_down")
#calculate the correlation scores
```

Table 3 shows the summaries of the two categorical variables. Single family households make up approximately two-thirds of the survey responses in this region and only 0.5% (8) of responses came from households formed from non-related individuals. Of the 1725 households, less than a quarter (21.4%) had a female head of household.

```{r categorical summaries, fig.align='center', fig.pos="H"}

data.cat<-as.data.frame(cbind(data$Household.Head.Sex, data$Type.of.Household))
colnames(data.cat)<-c("Household.Head.Sex", "Type.of.Household")

table_sex<-data.cat %>% 
  tabyl(Household.Head.Sex) %>%
  adorn_totals("row") %>%
  adorn_pct_formatting();

table_household<- data.cat %>% 
  tabyl(Type.of.Household) %>%
  adorn_totals("row") %>%
  adorn_pct_formatting(); 
knitr::kable(table_sex, booktabs = TRUE, caption = "Summary of Categorial Explanatory Variables")
knitr::kable(table_household, booktabs = TRUE, align = "c")
```

The pairs plot in Figure 2 is colour coded to illustrate any differences between the distributions of the quantitative variables when the head of household sex is included as a factor. The plots suggest the sex of the head of household may impact the number of family members in the household and the age of the head of the household.

```{r pairs, echo=FALSE, out.width= '100%', fig.cap="Paired plots of the variables",fig.align = "center"}
ggpairs(data.score, aes(colour = as.factor(data$Household.Head.Sex), alpha = 0.4), upper = list(continuous = wrap(ggally_cor, size = 2)))
#to get pairs plots.
```


***
\newpage

# Analysis of Relationships between Covariates {#sec:ARC}

## The relationship between independent and dependent variables

We will explore whether nine variables related to households in the dataset have an impact on the number of people living in the house (Total.Number.of.Family.members). These nine variables are Annual household income, Annual expenditure by the household on food, Head of the households sex, Head of the households age, Relationship between the group of people living in the house, Floor area of the house, Age of the building, Number of bedrooms in the house and House electrification situation. 

First let's look at the scatterplot of the response variable versus the numerical variable.

```{r echo=FALSE, out.width= '100%', fig.align = "center"}
p1= ggplot(data, aes(x = Total.Household.Income,y=Total.Number.of.Family.members)) + 
  geom_jitter(width = 0.1, color="lightskyblue1") +
  labs(x = "Annual household income",y="Number of people living in the house")+
  theme(axis.title.x = element_text(size = 7), axis.title.y = element_text(size = 7))
p2= ggplot(data, aes(x = Total.Food.Expenditure, y = Total.Number.of.Family.members))+
  geom_jitter(width = 0.1, color="blue1") +
  labs(x = "Annual expenditure by the household on food",y="Number of people living in the house")+
  theme(axis.title.x = element_text(size = 6), axis.title.y = element_text(size = 7))
p3= ggplot(data, aes(x = Household.Head.Age, y = Total.Number.of.Family.members)) + 
  geom_jitter(width = 0.1, color="lightskyblue1") +
  labs(x = "Head of the households age(years)",y="Number of people living in the house")+
  theme(axis.title.x = element_text(size = 7), axis.title.y= element_text(size = 7))
p4= ggplot(data, aes(x = House.Floor.Area, y = Total.Number.of.Family.members)) + 
  geom_jitter(width = 0.1, color="blue1") +
  labs(x = "Floor area of the house (m2)",y="Number of people living in the house")+
  theme(axis.title.x = element_text(size = 7), axis.title.y = element_text(size = 7))
p5= ggplot(data, aes(x = House.Age, y = Total.Number.of.Family.members)) + 
  geom_jitter(width = 0.1, color="lightskyblue1") +
  labs(x = "Age of the building(years)",y="Number of people living in the house")+
  theme(axis.title.x = element_text(size = 7), axis.title.y = element_text(size = 7))
grid.arrange(p1, p2,p3,p4,p5, ncol = 3)
```

## Gender & Age

As highlighted by the pairs plot, there appears to be a relationship between the sex and age of the head of the household. 

```{r gender data}
data.gender <- data %>%
  select(Household.Head.Sex, Household.Head.Age) #subsetting data to select variables of interest
```

The minimum and maximum ages of household heads do not appear to differ greatly according to the individuals' sex, however they do differ at the 25th, 50th and 75th percentiles with male heads of households being consitently younger than their female counterparts. The standard deviation is also greater for the female group, but the substantially smaller group size for females may contribute to this larger variation.

```{r summaries of age by sex}
age.gender<- data.gender %>% 
  group_by(Household.Head.Sex)%>%
  summarize(n=n(),Mean=round(mean(Household.Head.Age),digits=2), St.Dev=round(sd(Household.Head.Age),digits=2),
Min=min(Household.Head.Age), Q1 = quantile(Household.Head.Age,0.25), Median=median(Household.Head.Age),
Q3 = quantile(Household.Head.Age,0.75), Max=max(Household.Head.Age)) %>%
kable(caption = 'Summary statistics on the age of household heads by sex.') %>%
kable_styling(latex_options = "hold_position"); age.gender
```

The boxplot in Figure 4 illustrates the previously summarised data. The boxplot identifies the two oldest male head of households as outliers (shown by the points above the whisker), however within the context of the data and when compared to the ages of female head of household boxplot, these ages do not appear unreasonable or unrealistic.

```{r boxplot of age by gender, echo=FALSE, out.width= '80%', fig.cap="Boxplots of Head of Household Age stratified by Sex",fig.align = "center"}
boxplot1<- ggplot(data = data.gender, aes(x = Household.Head.Sex, y = Household.Head.Age, fill = Household.Head.Sex)) +
  geom_boxplot() +
  labs(x = "Head of Household Sex", y = "Head of Household Age", title="Age of Head of Household by Sex")+ 
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))
print(boxplot1 + scale_fill_manual(values=c("lightskyblue1", "blue1")))
```

The following Mann-Whitney U-test shows that there is a statistically significant difference in the median ages of male and female head of households at a 5% level.

```{r test for significant difference between ages of sexes}
wilcox.test(data.gender$Household.Head.Age~data.gender$Household.Head.Sex)
```

## Household Income and Food Expenditure

```{r balance}
data.balance <- data %>%
  select(Total.Household.Income, Total.Food.Expenditure) #subsetting data by selecting variables of interest
```

Figure 5 shows a boxplot of household incomes suggests a heavily skewed distribution with many outliers at the upper end of the distribution.

```{r balance boxplot,eval = TRUE, fig.align='center', fig.cap="Household Incomes in 10000 Phillipine Pesos.", out.width='80%', fig.pos = "H"}
ggplot(data.balance, aes(y=Total.Household.Income)) +
  geom_boxplot(color="black", fill="royalblue1") +
  labs(x="",y="Total Household Income (10000 Phillipine Peso)", title="Total Household Income (in 10000 Phillipine Pesos)") +
  theme(plot.title=element_text(hjust=0.5)) +
  scale_x_discrete(labels=NULL)
```

The following boxplot in Figure 6 shows the log transformed household income and shows there are still several outliers following the transformation. 

```{r balance boxplot2, eval = TRUE, fig.align='center', fig.cap="Boxplot of log transformed Incomes.", out.width='80%', fig.pos = "H"}
ggplot(data.balance, aes(y=log(Total.Household.Income))) +
  geom_boxplot(color="black", fill="royalblue1") +
  labs(x="",y="Log Total Household Income", title="Log Total Household Income") +
  theme(plot.title=element_text(hjust=0.5)) +
  scale_x_discrete(labels=NULL)
```

The scatterplot in Figure 7 of household income against total food expenditure suggests a positive correlation but the fitted model may be being heavily influenced by the extreme values, particularly by one extreme point.

```{r balance_plot, eval = TRUE, fig.align='center', fig.cap="Scatterplot of Income against Food Expenditure.", out.width='80%', fig.pos = "H"}
ggplot(data = data.balance, aes(x = Total.Household.Income, y = Total.Food.Expenditure)) +  geom_point(color="royalblue1", position="jitter", alpha=0.5) +
  labs(x = "Total Household Income (10000 Peso)", y = "Total Food Expenditure (10000 Peso)", title="Scatterplot of Total Household Income against Food Expenditure ") +
  geom_smooth(method = glm, se = FALSE, color="black") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
```

Figure 7 again highlights a possible outlier in terms of income, this could be a data entry error or just an outlier at the maximum. Removing this observation from the data set and plotting provides the following scatter diagram in Figure 8. This plot reconfirms the suggested positive correlation, but there is still an imbalance in the amount of data available at different levels of income. For example, most data is available for incomes between 0 and 750000 peso, but far fewer data points occur above this income level.

```{r balance without outlier, eval = TRUE, fig.align='center', fig.cap="Scatterplot of Income and Food Expenditure with extreme value removed.", out.width='80%', fig.pos = "H"}
index<-which.max(data.balance$Total.Household.Income)
balance_without_outlier<- data.balance[-index,]
ggplot(data = balance_without_outlier, aes(x = Total.Household.Income, y = Total.Food.Expenditure)) +
  geom_point(color="royalblue1", position="jitter", alpha=0.5) +
  labs(x = "Total Household Income (10000 Phillipine Pesos)", y = "Total Food Expenditure (10000 Phillipine Pesos", title="Income and Food Expenditure without Extreme Value") +
  geom_smooth(method = glm, se = FALSE, color="black") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
```

## Number of Family Members & Head of Household Sex

```{r}
data.sex_number <- data %>%
  select(Household.Head.Sex, Total.Number.of.Family.members)
```

```{r boxplot of sex and members, eval = TRUE, fig.align='center', fig.cap="Number of Members in Household by Sex of Head of Household", out.width='80%', fig.pos = "H"}
boxplot2<-ggplot(data = data.sex_number, aes(x = Household.Head.Sex, y = Total.Number.of.Family.members, fill = Household.Head.Sex)) +
  geom_boxplot() +
  labs(x = "Sex of Head of Household", y = "Number of Members in Household", title = "Boxplot of Household Size by Sex of Head of Household")+ 
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
print(boxplot2 + scale_fill_manual(values=c("lightskyblue1", "blue1")))
```

Hence we can see from Figure 9 that households with a male head appear to have a greater number of family members on average than those with a female head, as the male group has larger values for the first and third quartiles and the median. However there is overlap between the two groups central IQR and so the distributions may not be significantly different.


Figure 9 shows that an extended family household or one formed by non-related individuals is more likely to have a female head, whereas a larger proportion of single family households have male heads. 

```{r barplot of sex by type of household, eval = TRUE, fig.align='center', fig.cap="Barplot of household head's sex by type of household", out.width='80%', fig.pos = "H"}
barplot1<- ggplot(data = data, aes(x = Type.of.Household, group = Household.Head.Sex)) +
  geom_bar(aes(y = ..prop.., fill = Household.Head.Sex), stat = "count", position = "dodge") +
  labs(x = "Type of Household", y = "Proportion")
print(barplot1 + scale_fill_manual(values=c("lightskyblue1", "blue1")))
```


***
\newpage

# Exploratory Model Analysis {#sec:EMA}

## GLM Model Exploration

Prior to exploring any models, the outlier for Total Household Income and corresponding measurements for the other variables from this individual are removed. 

```{r removing outlier}
data<-data[-index,]
```

The following code identifies which explanatory variables would be included to produce the best models of different sizes, in this instance the maximum number of variables specified is ten. The output suggests the first predictor to be included is the total food expenditure in 10000 Phillipine pesos, and the last to be included is the binary variable Electricity that identifies if a household has electricity.
Comparing each of the ten models produced by BIC, CP and adjusted R^2 criteria is inconclusive as each implies a different model is best.

```{r assessing variables for inclusion}
models <- regsubsets(Total.Number.of.Family.members~., data = data, nvmax = 10)
summary(models)
res.sum <- summary(models)
selection.criteria<- c(Adj.R2 = which.max(res.sum$adjr2), CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)); selection.criteria
```


***
\newpage


# Formal Model Analysis {#sec:FMA}

## Poisson Regression model

The response variable of the Total Number of Family Members (or members of the household) can be viewed as a count and therefore a Poisson Regression model is considered. For a Poisson model to be suitable, the mean and variance should be equal and so these assumptions are checked first.

```{r poisson mean and variance check}
data$Total.Number.of.Family.members<-as.integer(data$Total.Number.of.Family.members)
members.mean<-mean(data$Total.Number.of.Family.members)
members.var<-var(data$Total.Number.of.Family.members)
meanandvar<- c(members.mean,members.var)
names(meanandvar)<-c("Mean", "Variance"); meanandvar%>%kable(col.names = "", caption="Mean and Variation of Response Variable")
```

From the table 5, The variation of total number of family members is only marginally larger than the mean of total number of family members, thus, the possibility of over-dispersion in our model is not a significant issue.

```{r full poisson model}
model_poisson_full <- glm(Total.Number.of.Family.members ~ Total.Household.Income +
                Total.Food.Expenditure + Household.Head.Age + House.Floor.Area + House.Age + Number.of.bedrooms + Electricity + Household.Head.Sex + Type.of.Household, family = poisson(link = "log"), data = data)

model_poisson_full %>%
  summary()
```

The poisson model fitted with all possible covariates concludes there are six statistically significant predictors at the 5% level. These are the total household income and food expenditure, the age and gender of the head of the household, the age of the house and if it is a single family household. 
Table 5 shows the estimates and the lower and upper bounds of the 95% confidence intervals for the regression parameters. The rows containing significant predictors, and so where the confidence intervals do not include 0, are highlighted. 

```{r table of estimates and confidence intervals, eval=TRUE}
poisson.int<- as.data.frame(confint(model_poisson_full))
poisson.int[,1]<-poisson.int[,1]
poisson.int[,3]<-poisson.int[,2]
poisson.int[,2]<- model_poisson_full$coefficients
colnames(poisson.int)<- c("Lower Bound","Estimate","Upper Bound"); 
poisson.int%>% kable(caption = "Estimates and the corresponding 95% Confidence Intervals, with significant predictors highlighted.") %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(c(1,2,3,4,6,9,10), background  = "#A1E8F1", color="black")
```


We refit the model to include just the previously identified significant covariates and again evaluated the 95% confidence intervals for the estimated parameters, these values can be seen in Table 6. The intercept term of 1.436 is simply a positional constant due to the context of the variables. The negative coefficient of Total Household Income shows that for every additional 10000 peso, the number of household members is expected to decrease by 0.002. The coefficient of Total Food Expenditure suggests that for an increase of 10000 peso in spending, there is an expected 0.048 more members in the household. The coefficients of Head of Household age and the Age of the Building are both negative (-0.003 and -0.002 respectively) showing that an older head of the household or older building is linked to fewer members in a household. A Single Family household is expected to have 0.350 fewer members than the baseline category of an extended family household, and households with a male head will have 0.222 members more than their female counterparts.

```{r poisson model with significant variables}
model_poisson_significant <- glm(Total.Number.of.Family.members ~ Total.Household.Income + Total.Food.Expenditure + Household.Head.Age + House.Age + Household.Head.Sex + Type.of.Household, family = poisson(link = "log"), data = data)
model_poisson_significant %>%
  summary()
```

```{r table of estimates and confidence intervals sig, eval=TRUE}
poisson.sig.int<- as.data.frame(confint(model_poisson_significant))
poisson.sig.int[,1]<-poisson.sig.int[,1]
poisson.sig.int[,3]<-poisson.sig.int[,2]
poisson.sig.int[,2]<- model_poisson_significant$coefficients
colnames(poisson.sig.int)<- c("Lower Bound","Estimate","Upper Bound"); 
poisson.sig.int%>% kable(caption = "Estimates of regression parameters and the corresponding 95% Confidence Intervals") %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(c(1,2,3,4,5,6,7), background = "#A1E8F1", color="black")
```


```{r summary plot, eval = TRUE, fig.align='center', fig.cap="Summary of Coefficients for each fitted Poisson Model", out.width='80%', fig.pos = "H"}
plot_summs(model_poisson_full,model_poisson_significant, scale=TRUE, exp = TRUE, model.names = c("Full", "Significant\nCovariates"), point.shape = FALSE, colors=c("lightskyblue", "blue"))
```


```{r model comparison 1}
Models <- c('Full Model','Significant Factors Model')
bind_rows(glance(model_poisson_full), glance(model_poisson_significant),.id="Model") %>%
  select(Model,AIC,BIC) %>%
  mutate(Model=Models) %>%  
  kable(booktabs = TRUE,digits = 2, caption = "Comparison of Fitted Poisson Models", format="pipe") %>% 
  kable_styling(latex_options = 'HOLD_position', ) # to get a table of AIC & BIC
```

From table8, we got the AIC value of two model do not have significant differemt, however, the BIC value of significant factors model is lower than the full model. Thus, we decided to choose the significant factors model.

The poisson regression model that will be fitted to the data is as follows:
$$log(\tilde{\lambda_i}) = \alpha + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} + \widehat{\beta}_{\mbox{M}} \cdot \mathbb{I}_{\mbox{M}}(i) + \epsilon_i, ~~~~ \epsilon \sim N(0, \sigma^2),$$
where

 - $log(\tilde{\lambda})$ is the Total Number of Family Members of the $i^{th}$ individual;
 - $x_1$ is the Total Household Income in pesos;
 - $x_2$ is the Total Food Expenditure in pesos;
 - $x_3$ is the Household Head's Age in years;
 - $x_4$ is the House's Age in years;
 - $\alpha$ is the intercept and positions the best-fitting plane in 3D space;
 - $\beta_1$ is the coefficient for the first explanatory variable $x_1$;
 - $\beta_2$ is the coefficient for the second explanatory variable $x_2$;
 - $\beta_3$ is the coefficient for the second explanatory variable $x_3$;
 - $\beta_4$ is the coefficient for the second explanatory variable $x_4$;
 - $\widehat{\beta}_{\mbox{M}}$ is the difference in the mean total number of family members of a male household head relative to the female household head; and
 - $\epsilon_i$ is the $i^{th}$ random error component; and
 - $\mathbb{I}_{\mbox{F}}(i)$ is an indicator function such that
 
$$\mathbb{I}_{\mbox{M}}(i)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if the household head of} ~ i \mbox{th observation is Male},\\
0 ~~~ \mbox{Otherwise}.\\
\end{array}
\right.$$


```{r pred plot, eval = TRUE, fig.align='center', fig.cap="Predicted Numbers of Household Members", out.width='80%', fig.pos = "H"}
data$phat <- predict(model_poisson_full, type = "response")
pred.plot<- ggplot(data, aes(x = Total.Food.Expenditure, y = phat, colour = Household.Head.Sex)) +
  geom_point(aes(y = Total.Number.of.Family.members), position = position_jitter(h = 0.15)) +
  geom_smooth(method = glm, se = FALSE) +
  labs(x = "Total Food Expenditure (10000 pesos)", y = "Expected Number of Family Members")
print(pred.plot + scale_colour_manual(values=c("lightskyblue", "blue")))
```

```{r compare plot, eval = TRUE, fig.align='center', fig.cap="Scatterplot Numbers of Household Members and number of family members", out.width='80%', fig.pos = "H"}
ggplot(data, aes(x = Total.Food.Expenditure, y = Total.Number.of.Family.members, colour = Household.Head.Sex)) +
  geom_point(aes(y = Total.Number.of.Family.members), position = position_jitter(h = 0.15)) +
  geom_smooth(method = glm, se = FALSE) +
  labs(x = "Total Food Expenditure (10000 pesos)", y = "Number of Family Members")
```


# Conclusions {#sec:Conc}

In conclusion, 


***
